---
title: "Spanish CDI explorations"
author: "Paulina & Mike"
date: "2022-10-13"
output: html_document
---

# Intro

Goal of this project is to use the five Spanish CDI datasets in Wordbank to try and investigate dialect variation in Spanish language acquisition. 

Here are some potential questions:

* Do the sumscores across the intersecting items look the same at the population level (correcting for demographics)?
* Do individual common items have similar psychometric / developmental properties?
* What are the properties of items with the same unilemma but different item definitions?
* What are the properties of items that are not shared across dialects? (Could also compare Spanish (Mexican) between monolingual and bilingual populations)


```{r setup}
library(tidyverse)
library(wordbankr)
```

# Data loading

Start with summary scores. 

```{r}
eu_ws <- get_administration_data(language = "Spanish (European)", 
                                 form = "WS", 
                                 include_demographic_info = TRUE)
mx_ws <- get_administration_data(language = "Spanish (Mexican)", 
                                 form = "WS", 
                                 include_demographic_info = TRUE)
pr_ws <- get_administration_data(language = "Spanish (Peruvian)", 
                                 form = "WS", 
                                 include_demographic_info = TRUE)
ar_ws <- get_administration_data(language = "Spanish (Argentinian)", 
                                 form = "WS", 
                                 include_demographic_info = TRUE)

sp_ws <- bind_rows(eu_ws, 
                   mx_ws, 
                   pr_ws, 
                   ar_ws)
```


```{r}

```

