---
title: "Spanish CDI explorations"
author: "Paulina & Mike"
date: "2022-10-13"
output: html_document
---

# Intro

Goal of this project is to use the five Spanish CDI datasets in Wordbank to try and investigate dialect variation in Spanish language acquisition. 

Here are some potential questions:

* Do the sumscores across the intersecting items look the same at the population level (correcting for demographics)?
* Do individual common items have similar psychometric / developmental properties?
* What are the properties of items with the same unilemma but different item definitions?
* What are the properties of items that are not shared across dialects? (Could also compare Spanish (Mexican) between monolingual and bilingual populations)


```{r setup}
library(tidyverse)
library(wordbankr)
library(arm)
```

# Data loading

Start with summary scores. 

```{r}
eu_ws <- get_administration_data(language = "Spanish (European)", 
                                 form = "WS", 
                                 include_demographic_info = TRUE)
mx_ws <- get_administration_data(language = "Spanish (Mexican)", 
                                 form = "WS", 
                                 include_demographic_info = TRUE)
pr_ws <- get_administration_data(language = "Spanish (Peruvian)", 
                                 form = "WS", 
                                 include_demographic_info = TRUE)
ar_ws <- get_administration_data(language = "Spanish (Argentinian)", 
                                 form = "WS", 
                                 include_demographic_info = TRUE)

sp_ws <- bind_rows(eu_ws, 
                   mx_ws, 
                   pr_ws, 
                   ar_ws)
```

Make a plot!

```{r}
ggplot(sp_ws, aes(x = age, y = production)) + 
  geom_jitter(width = .2, alpha = .2) + 
  geom_smooth() + 
  facet_wrap(~language)
```


# Comparison on the intersection of items

QUESTION: Do the sumscores across the intersecting items look the same at the population level (correcting for demographics)?

```{r}
langs <- c("Spanish (European)", "Spanish (Mexican)", "Spanish (Peruvian)", "Spanish (Argentinian)")

d_ws <- map_df(langs, function(x) get_instrument_data(language = x, 
                                                      form = "WS", 
                                                      administration_info = TRUE, 
                                                      item_info = TRUE))
```

Find the overlapping unilemmas.

For now, pull those unilemmas that are 1) in all languages, 2) only once in each language. 

```{r}
items <- map_df(langs, function(x) get_item_data(language = x, form = "WS"))

intersection <- items |>
  group_by(uni_lemma) |>
  summarise(n_langs = length(unique(language)), 
            n = n()) |>
  filter(n_langs == 4, n == 4) |>
  pull(uni_lemma)
# 224 common items
``` 

Filter data and replot. 

```{r}
ms_ws <- d_ws |>
  filter(uni_lemma %in% intersection) |>
  group_by(child_id, language, age) |>
  summarise(produces = sum(produces))

ggplot(ms_ws, aes(x = age, y = produces)) + 
  geom_jitter(width = .2, alpha = .2) + 
  geom_smooth() + 
  facet_wrap(~language)
```



# Comparison of developmental properties

QUESTION: Do individual common items have similar psychometric / developmental properties?

```{r}
source("scripts/fit_models.R")

wb_data <- d_ws |> 
  filter(uni_lemma %in% intersection) |>
  group_by(uni_lemma, language, age) |> 
  summarise(total = n(),
            num_true = sum(produces, na.rm = TRUE))

aoas <- fit_aoas(wb_data)
```

```{r}
ggplot(data = aoas) +
  geom_histogram(aes(x = aoa))+ 
  facet_wrap(~language)
```

Calculate correlations between languages

```{r}
cor_data <- aoas |> 
  pivot_wider(id_cols = uni_lemma, 
              names_from = language,
              values_from = aoa) |> 
  ungroup()

correl <- cor(cor_data |> dplyr::select(-"uni_lemma"), use = "complete.obs")
```

Plot correlogram
```{r}
library(corrgram)
corrgram(correl, type = "cor", panel = panel.cor)
```

```{r}
plot_data <- cor_data |> 
  pivot_longer(cols = c(`Spanish (Argentinian)`, `Spanish (Mexican)`, `Spanish (Peruvian)`), 
               names_to = "Dialect")
ggplot(plot_data, aes(x = `Spanish (European)`, y = value, col = Dialect)) + 
  geom_abline(slope = 1, intercept = 0, lty = "dashed", col = "#444444") +
  geom_point(alpha=.3) +
  geom_smooth(method = "lm") +
  theme_classic() + 
  theme(legend.position = "bottom") +
  labs(x = "Spanish (European) AoA",
       y = "Spanish (Latin American) AoA") +
  coord_cartesian(xlim = c(0, 40), ylim = c(0, 40))
```

Calculate differences in age of acquisition (AoA) between all dialects for each unilemma
```{r}
clean_aoas <- aoas |>
  dplyr::select(uni_lemma, language, aoa) |>
  pivot_wider(names_from = language, values_from = aoa)

difference_argentinian_european <- data.frame(difference_argentinian_european = abs(c(clean_aoas$`Spanish (Argentinian)`- clean_aoas$`Spanish (European)`)))

difference_argentinian_mexican <- data.frame(difference_argentinian_mexican = abs(c(clean_aoas$`Spanish (Argentinian)`- clean_aoas$`Spanish (Mexican)`)))

difference_argentinian_peruvian <- data.frame(difference_argentinian_peruvian = abs(c(clean_aoas$`Spanish (Argentinian)`- clean_aoas$`Spanish (Peruvian)`)))

difference_european_mexican <- data.frame(difference_european_mexican = abs(c(clean_aoas$`Spanish (European)`- clean_aoas$`Spanish (Mexican)`)))

difference_european_peruvian <- data.frame(difference_european_peruvian = abs(c(clean_aoas$`Spanish (European)`- clean_aoas$`Spanish (Peruvian)`)))

difference_mexican_peruvian <- data.frame(difference_mexican_peruvian = abs(c(clean_aoas$`Spanish (Mexican)`- clean_aoas$`Spanish (Peruvian)`)))

difference_AoA <- data.frame(uni_lemma = c(clean_aoas$uni_lemma), difference_argentinian_european, difference_argentinian_mexican, difference_argentinian_peruvian, difference_european_mexican, difference_european_peruvian, difference_mexican_peruvian)
```